Etox-Base: A tool to derive exposure endpoints from chemical test results

### 2019-02-09 article/article.tex
Updates from Overleaf

@@

Generally it has to be stated here that the returned values are subject to change, as new tests will be constantly incorporated into the \etoxbase{}. However, we expect values of well tested chemical-organism combinations (i.e. high N <MAYBE PUT NUMBER HERE - CITATION>) to be relatively stable. Yet, returned values from the \etoxbase{} are certainly influenced by individual tests procedures and characteristics, such as pH, temperature or conductivity to just name a few. However, using the median or the geometric mean as an aggregate allows for an adequate estimation of the central tendency of the toxicity of a chemical towards an organism group. The geometric mean is recommended, as it is in comparison to the arithmetic mean considerably less influenced by outliers and is suitable for skewed data. Also, the geometric mean is preferable in contrast to the median, since the median completely ignores the influence of large or small values, making it unreliable for small data sets <CITATION GEOMETRIC MEAN>.

@@

SSDs aim to extrapolate from species to the community level while not ignoring environmental variables (e.g. pH, temperature, etc.) which can effect the toxicity of a specific chemical greatly \citep{posthuma_species_2002}. For a large number of the \epa{} tests, environmental variables are not recorded (See \ref{table:meta-variables} for proportions of missing entries per variable). Hence to some extent the reported test results inherit uncertainty. In this context we also call for more emphasis on machine-readability when publishing ecotoxicological test results <CITATION ON AS OF HOW MANY DATA POINTS MACHINES ARE NEEDED>. A lot of important information is still confined in continuous text of articles and therefore not ascertainable for large scale analyses.

@@

\section*{Figure Legends}

>>>>

\pagebreak

@@

Generally it has to be stated that the returned values are subject to change, as new tests will be constantly incorporated into the \etoxbase{}. However, we expect values of well tested chemical-organism combinations to be relatively stable. The returned values are certainly influenced by individual tests characteristics, such as pH, temperature or conductivity to just name a few, which influences the effect relationship between chemicals and organisms \citep{rosenkrantz_influence_2013,li_temperature_2011}. Unfortunately the EPA ECOTOX data base has only rare records on test parameters, which prevents incorporating such parameters in an aggregation <proportions of available data: Temperature:77\%, pH:56\%, hardness:27\%, dissolved oxygen:18\%, Alkalinity:15\%, salinity:9\%, others:<=5\%>. However, using the median or the geometric mean as an aggregate allows for an adequate estimation of the central tendency of the toxicity of a chemical towards an organism group. The geometric mean is recommended, as it is in comparison to the arithmetic mean considerably less influenced by outliers and is suitable for skewed data. Also, the geometric mean is preferable in contrast to the median, since the median completely ignores the influence of large or small values, making it unreliable for small data sets <CITATION GEOMETRIC MEAN>.

@@

\pagebreak

@@

\pagebreak
